Reasoning About a Machine with Local Capabilities

### 2018-05-08 toplas/preamble-illu.tex
preamble

% Active adversary
\newcommand{\actadv}[4][]{
  \ifthenelse{\equal{#1}{}}{
    \draw[fill=white] #2 rectangle #3 node[pos=.5] {};
    \draw ($#2 + (3,1.5)$) node[devil,mirrored,minimum size=1cm] {};
    \draw[fill=white, fill opacity=0.5] #2 rectangle #3 node[pos=.5] {};
    \draw #2 rectangle #3 node[pos=.5] {\footnotesize #4};
  }{
    \onlyenv<#1>
    \draw[fill=white] #2 rectangle #3 node[pos=.5] {};
    \draw ($#2 + (3,1.5)$) node[devil,mirrored,minimum size=1cm] {};
    \draw[fill=white, fill opacity=0.5] #2 rectangle #3 node[pos=.5] {};
    \draw #2 rectangle #3 node[pos=.5] {\footnotesize #4};
    \endonlyenv
  }
}

% Inactive adversary
\newcommand{\inactadv}[4][]{
  \ifthenelse{\equal{#1}{}}{
    \draw[fill=white] #2 rectangle #3 node[pos=.5] {};
    \draw ($#2 + (3,1.5)$) node[devil,mirrored,minimum size=1cm] {};
    \draw[fill=white, fill opacity=0.4] #2 rectangle #3 node[pos=.5] {};
    \draw[fill=gray, fill opacity=0.5] #2 rectangle #3 node[pos=.5] {};
    \draw #2 rectangle #3 node[pos=.5] {\footnotesize #4};
  }{
    \onlyenv<#1>
    \draw[fill=white] #2 rectangle #3 node[pos=.5] {};
    \draw ($#2 + (3,1.5)$) node[devil,mirrored,minimum size=1cm] {};
    \draw[fill=white, fill opacity=0.4] #2 rectangle #3 node[pos=.5] {};
    \draw[fill=gray, fill opacity=0.5] #2 rectangle #3 node[pos=.5] {};
    \draw #2 rectangle #3 node[pos=.5] {\footnotesize #4};
    \endonlyenv
  }
}

@@

\newcommand{\stdstackstart}{
  \scope
    \clip (-.1,-.1) rectangle (6.1,15.1);
    \fill[fill=white] (0,0) rectangle (6,15);
    \draw (0,0) -- (0,15);
    \draw (6,0) -- (6,15);
    \draw[fill=gray!50] (0,-.5) rectangle (6,2.5) node[pos=.5,color=black] {\footnotesize higher stack frames...};
  \endscope
  % \draw[->] (-2,0) -- node[midway,sloped,above] {stack grows upward} (-2,15);
  \draw (-1.5,0) node {};
  \draw (-1.5,15) node {};
}

@@

>>>>

% Active adversary
\newcommand{\actadv}[4][]{
  \ifthenelse{\equal{#1}{}}{
    \draw[fill=white] #2 rectangle #3 node[pos=.5] {};
    \draw ($#2 + (2.25,1.5)$) node[devil,mirrored,minimum size=1cm] {};
    \draw[fill=white, fill opacity=0.5] #2 rectangle #3 node[pos=.5] {};
    \draw #2 rectangle #3 node[pos=.5,align=center] {\footnotesize #4};
  }{
    \onlyenv<#1>
    \draw[fill=white] #2 rectangle #3 node[pos=.5] {};
    \draw ($#2 + (3,1.5)$) node[devil,mirrored,minimum size=1cm] {};
    \draw[fill=white, fill opacity=0.5] #2 rectangle #3 node[pos=.5] {};
    \draw #2 rectangle #3 node[pos=.5] {\footnotesize #4};
    \endonlyenv
  }
}

% Inactive adversary
\newcommand{\inactadv}[4][]{
  \ifthenelse{\equal{#1}{}}{
    \draw[fill=white] #2 rectangle #3 node[pos=.5] {};
    \draw ($#2 + (2.25,1.5)$) node[devil,mirrored,minimum size=1cm] {};
    \draw[fill=white, fill opacity=0.4] #2 rectangle #3 node[pos=.5] {};
    \draw[fill=gray, fill opacity=0.5] #2 rectangle #3 node[pos=.5] {};
    \draw #2 rectangle #3 node[pos=.5] {\footnotesize #4};
  }{
    \onlyenv<#1>
    \draw[fill=white] #2 rectangle #3 node[pos=.5] {};
    \draw ($#2 + (3,1.5)$) node[devil,mirrored,minimum size=1cm] {};
    \draw[fill=white, fill opacity=0.4] #2 rectangle #3 node[pos=.5] {};
    \draw[fill=gray, fill opacity=0.5] #2 rectangle #3 node[pos=.5] {};
    \draw #2 rectangle #3 node[pos=.5] {\footnotesize #4};
    \endonlyenv
  }
}

@@

\newcommand{\stdstackstart}{
  \scope
    \clip (-.1,-.1) rectangle (4.6,11.1);
    \fill[fill=white] (0,0) rectangle (4.5,11);
    \draw (0,0) -- (0,11);
    \draw (4.5,0) -- (4.5,11);
    \draw[fill=gray!50] (0,-.5) rectangle (4.5,2)
    node[pos=.5,color=black,align=center,yshift=0.1cm] {\footnotesize Higher
      stack\\\footnotesize frames...};
  \endscope
  % \draw[->] (-2,0) -- node[midway,sloped,above] {stack grows upward} (-2,15);
  \draw (-1.5,0) node {};
  \draw (-1.5,15) node {};
}

@@

%%% Local Variables:
%%% TeX-master: "paper"
%%% End:
